Crop diversification in a game against nature

### 2020-01-22 risk-percption.Rmd
new payoff matrix

```{r}
#wheat_dry <- 0
#wheat_wet <- 1.6
#barley_dry <- 0.93
#barley_wet <- 1.18

wheat_dry <- 30
wheat_normal <- 60
wheat_wet <- 70

barley_dry <- 50
barley_normal <- 50
barley_wet <- 40
```

>>>>

```{r}
wheat_dry <- 0
wheat_normal <- 1.5
wheat_wet <- 1.7

barley_dry <- 0.8
barley_normal <- 1
barley_wet <- 0.5
```

```{r}
readxl::read_xls('41467_2014_BFncomms4953_MOESM580_ESM.xls', range = 'A2:O370') %>%
  select(`Site Location`, Taxon, `ky cal BP`, `GY (t*ha-1)`) %>%
  filter(!is.na(`GY (t*ha-1)`)) %>% 
  group_by(`Site Location`, Taxon) %>%
  summarise(yield_mean = mean(`GY (t*ha-1)`)) %>%
  spread(Taxon, yield_mean)
```
